Monitoring Time Series With Missing Values:\\a Deep Probabilistic Approach

### 2022-02-16 paper.tex
minor

We thank PUB+ for providing computational facilities for
conducting the empirical evaluation. David Tolpin is partially
supported by Israel-U.S. Industrial Research and Development
Foundation's Cybersecurity technology for critical power
infrastructure AI-based centralized defense and edge resilience
project.

>>>>

We thank PUB+ for providing computational facilities for
conducting the empirical evaluation. David Tolpin is partially
supported by Israel-U.S. Industrial Research and Development
Foundation's \textit{Cybersecurity technology for critical power
infrastructure AI-based centralized defense and edge resilience}
project.
